Key Derivation From Noisy Sources With More Errors Than Entropy

### 2014-09-23 trunk/constantRate/ConstCompFuzzExt-reorg.tex
modifying abstract

\begin{abstract}
Fuzzy extractors convert a noisy source of entropy into a consistent uniformly-distributed key.  In the process of eliminating noise, they  lose some of the entropy of the original source---in the worst case, as much as the logarithm of the number of correctable error patterns. For many practical sources, the error tolerance necessary to achieve reliable key derivation is larger than the entropy of the source.  Unfortunately, it is impossible to provide security for all sources with this property.  Most known approaches for building fuzzy extractors work in the worst case and cannot be used when a source has \emph{more errors than entropy}.

In this work, we exploit source structure to construct fuzzy extractors for large classes of sources with more errors than entropy.  Our constructions are for the Hamming metric over symbols of some alphabet .  We present both information-theoretic and computational constructions.

Our first construction is information-theoretic and corrects a constant fraction of Hamming errors over a super-constant size alphabet.  In this construction, each symbol must contribute fresh entropy.

Our second and third constructions switch to computational security to provide additional features.  Our second construction supports the same type of sources as the first construction but also provides reusability.  A reusable fuzzy extractor can be safely reused across multiple noisy readings of the source~(Boyen, CCS 2004).  Previous reusable fuzzy extractors only provide security when the noise between repeated readings comes from a small and unrealistic class. Our construction is secure as long as the fuzzy extractor is secure on each individual reading. Unfortunately, this construction only corrects a sub-constant fraction of errors.  %Computational techniques allow us to show a very sshows that computational assu computationaprovide requires a constant fraction of symbols to have a constant amount of entropy conditioned on prior symbols. It corrects a sub-constant fraction of errors and supports super-constant size alphabets.  In addition, it is first construction of a reusable fuzzy extractor without assumption on the form of errors that occurs between reuse.  This is impossible in the information-theoretic setting for an arbitrary number of reuses~(Boyen, CCS 2004).

Our first two constructions require each symbol of the source to contribute fresh entropy.  Our third construction removes this requirement and allows symbols to be dependent.  This change requires a significantly larger alphabet.

The computational constructions can be implemented efficiently based on number-theoretic assumptions or assumptions on cryptographic hash functions.

\bigskip

@@

\paragraph{Our Contributions}
We provide the first constructions of fuzzy extractors that can be used for large classes of sources that have more errors than entropy.  Our constructions work for Hamming errors for strings $w$ of length $\gamma$ over some alphabet $\mathcal{Z}$. Naturally, as argued above, these constructions cannot work for all sources of a given entropy; each construction comes with a constraint on the sources for which it is secure\onote{consider adding here that the class of sources we can deal with (in all constructions) contains many natural sources (or something along these lines).}.  Table~\ref{tab:upper bounds} summarizes our constructions. \lnote{Note sure about the first line of this table. What does ``exploit distribution structure'' mean? Also, can we make it look a bit better? Perhaps center. Perhaps also remove some lines. Perhaps make "main feature" column the same part of speech in each entry.}
\onote{The table is confusing to me: all the constructions exploits distribution structure. In the second construction most symbols must contribute fresh entropy as well. Third construction is also reusable. Perhaps there is a better way to organize this information.}
Our first construction provides information-theoretic security.  It can correct a constant fraction of errors, but requires that a constant fraction of the symbols contribute fresh entropy, even conditioned on previous symbols. %It requires an alphabet size that is super constant in the security parameter. \lnote{keep this last sentence?}

@@

Finally, our third construction tolerates more errors than the second because it uses digital lockers that are unlocked by single symbols of $w$. Since we do not assume that every symbol has high individual entropy, hiding an entire $r$ in every locker then becomes too risky, Instead, we hide a single bit per locker (our actual construction uses point obfuscations, which are simpler to construct than digital lockers \onote{I would skip this since it does not make the result stronger}). To tolerate errors, these bits come from an error correcting code. To ensure an  adversary who learns some bits doesn't learn anything useful about $r$, we don't encode $r$ in the error-correcting code, but rather extract $r$ (using an information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractor) from the decoded string.

We emphasize that the obfuscation techniques we use are much weaker than general obfuscation, and can be instantiated quite efficiently under appropriate assumptions.
We need a strong version of point obfuscation/digital lockers that remain secure even when several obfuscations of correlated points are composed. The required notion is
%While the standard definition of obfuscation \cite{barak2001possibility} does not imply security under composition, we can base our construction on the relaxed notion \lnote{something is weird --- standard definition is not ok for composition , but a relaxed one is ok?} \bnote{In neither definition is composition implied by standalone security.  However it is known how to construct composable VGB obfuscation for the class of functions we need.}
composable \emph{virtual grey-box} obfuscation introduced in~\cite{bitansky2010strong} . Bitanski and Canetti construct composable obfuscation of point programs under particular number-theoretic assumptions~\cite{bitansky2010strong}. 
Additionally, such obfuscation can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1997towards}.

\paragraph{The Required Notion of Obfuscation} \onote{How about this paragraph instead of the one above?} Our constructions are base on obfuscation that is simulation-secure, however, we do not require full-fledged virtual black-box obfuscation \cite{barak2001possibility}. Instead, we rely on the relaxed notion of \emph{virtual grey-box} obfuscation\cite{bitansky2010strong}. We also require that the obfuscation remains secure even when several digital lockers of correlated points are composed.
Composable digital lockers with virtual grey-box security where constructed by Bitanski and Canetti under particular number-theoretic assumptions~\cite{bitansky2010strong}.

@@

\paragraph{Connection to General Obfuscation}
We note that fuzzy extractors for sources with errors than entropy can be trivially constructed from virtual grey-box obfuscation for the class of {\em proximity point programs}. A proximity point program $I_w(x)$ tests if $x$ is within Hamming distance $t$ of $w$. 
Recently, such obfuscation was constructed based on the strong assumption of {\em semantically secure graded encodings} \cite{PassTS13,BitanskyCKP14}.
This construction however, is still highly impractical, while the obfuscation used in this work can be instantiated quite efficiently under appropriate assumptions.
Additionally, the known obfuscation for proximity point programs is not known to be composable and therefore does not yield a reusable fuzzy extractor.

>>>>

\begin{abstract}
Fuzzy extractors convert a noisy source of entropy into the same uniformly distributed key~(Dodis et al., Eurocrypt 2004).  In the process of eliminating noise, they  lose some of the entropy of the original source---in the worst case, as much as the logarithm of the number of tolerated error patterns. For many practical sources, the error tolerance necessary to achieve reliable key derivation is larger than the entropy of the source.  Unfortunately, it is impossible to provide security for every source with this property.  Most known approaches for building fuzzy extractors work in the worst case and thus cannot be used when a source has \emph{more errors than entropy}.

Fortunately, practical sources contain useful structure.  In this work, we exploit distributional structure to construct fuzzy extractors for large classes of noisy sources with more errors than entropy.  
We show an information-theoretic construction and two computational constructions with added features.  Our constructions are for the Hamming metric over symbols of an alphabet.

\begin{itemize} \item \textbf{Information-theoretic}  Our first construction supports sources where each symbol contributes fresh entropy and corrects a constant fraction of Hamming errors over a super-constant size alphabet.

\item \textbf{Computational}
%By adding computational techniques we obtain constructions with additional features.  
Our second construction is also secure when each symbol contributes fresh entropy.  
Additionally, it is a reusable fuzzy extractor~(Boyen, CCS 2004).  A reusable fuzzy extractor allows multiple readings of the source to be enrolled securely.  Our construction is reusable if each reading is a supported source.  Previous reusable fuzzy extractors required the correlation between repeated readings to be drawn from a small and unrealistic class.  This construction corrects a sub-constant fraction of errors.  %Computational techniques allow us to show a very sshows that computational assu computationaprovide requires a constant fraction of symbols to have a constant amount of entropy conditioned on prior symbols. It corrects a sub-constant fraction of errors and supports super-constant size alphabets.  In addition, it is first construction of a reusable fuzzy extractor without assumption on the form of errors that occurs between reuse.  This is impossible in the information-theoretic setting for an arbitrary number of reuses~(Boyen, CCS 2004).

Our third construction strengthens the class of supported sources and corrects a constant fraction of errors.  It is secure when individual symbols have high entropy but may be arbitrarily correlated.  This change requires a significantly larger alphabet.

The computational constructions can be implemented efficiently based on number-theoretic assumptions or assumptions on cryptographic hash functions.
\end{itemize}

\medskip

@@

\paragraph{Our Contributions}
We provide the first constructions of fuzzy extractors that can be used for large classes of sources that have more errors than entropy.  Our constructions work for Hamming errors for strings $w$ of length $\gamma$ over some alphabet $\mathcal{Z}$. Naturally, as argued above, these constructions cannot work for all sources of a given entropy; each construction comes with a constraint on the sources for which it is secure\onote{consider adding here that the class of sources we can deal with (in all constructions) contains many natural sources (or something along these lines).}.  Table~\ref{tab:upper bounds} summarizes our constructions. \lnote{Note sure about the first line of this table. What does ``exploit distribution structure'' mean? Also, can we make it look a bit better? Perhaps center. Perhaps also remove some lines. Perhaps make "main feature" column the same part of speech in each entry.}
\onote{The table is confusing to me: all the constructions exploits distribution structure. In the second construction most symbols must contribute fresh entropy as well. Third construction is also reusable. Perhaps there is a better way to organize this information.}
\bnote{these comments are all valid.  I'm not sure what to do about it.  Maybe organize by techniques and then notes (for limitations and features?)}
Our first construction provides information-theoretic security.  It can correct a constant fraction of errors, but requires that a constant fraction of the symbols contribute fresh entropy, even conditioned on previous symbols. %It requires an alphabet size that is super constant in the security parameter. \lnote{keep this last sentence?}

@@

Finally, our third construction tolerates more errors than the second because it uses digital lockers that are unlocked by single symbols of $w$. Since we do not assume that every symbol has high individual entropy, hiding an entire $r$ in every locker then becomes too risky, Instead, we hide a single bit per locker. To tolerate errors, these bits come from an error correcting code. To ensure an  adversary who learns some bits doesn't learn anything useful about $r$, we don't encode $r$ in the error-correcting code, but rather extract $r$ (using an information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractor) from the decoded string.

%We emphasize that the obfuscation techniques we use are much weaker than general obfuscation, and can be instantiated quite efficiently under appropriate assumptions.
%We need a strong version of point obfuscation/digital lockers that remain secure even when several obfuscations of correlated points are composed. The required notion is
%%While the standard definition of obfuscation \cite{barak2001possibility} does not imply security under composition, we can base our construction on the relaxed notion \lnote{something is weird --- standard definition is not ok for composition , but a relaxed one is ok?} \bnote{In neither definition is composition implied by standalone security.  However it is known how to construct composable VGB obfuscation for the class of functions we need.}
%composable \emph{virtual grey-box} obfuscation introduced in~\cite{bitansky2010strong} . Bitanski and Canetti construct composable obfuscation of point programs under particular number-theoretic assumptions~\cite{bitansky2010strong}. 
%Additionally, such obfuscation can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1997towards}.

\paragraph{The Required Notion of Point Obfuscation} 
Our constructions use simulation-secure  obfuscation of digital lockers, however, we do not require full-fledged virtual black-box obfuscation~\cite{barak2001possibility}. Instead, we rely on the relaxed notion of \emph{virtual grey-box} obfuscation~\cite{bitansky2010strong}. We also require that the obfuscation remains secure even when several digital lockers of correlated points are composed.
Bitanski and Canetti constructed composable digital lockers with virtual grey-box security under particular number-theoretic assumptions~\cite{bitansky2010strong}.

@@

\paragraph{Connection to General Obfuscation}
We note that fuzzy extractors for sources with more errors than entropy can be trivially constructed from virtual grey-box obfuscation for the class of {\em proximity point programs}. A proximity point program $I_w(x)$ tests if $x$ is within distance $t$ of $w$. 
Recently, Bitansky et al.~\cite{BitanskyCKP14} constructed such obfuscation based on the strong assumption of {\em semantically secure graded encodings} \cite{PassTS13}.
The construction of Bitansky et al. is based on multilinear encoding and is  highly impractical.  The obfuscation used in this work can be instantiated quite efficiently under appropriate assumptions.
Additionally, the known obfuscation for proximity point programs is not known to be composable and therefore does not yield a reusable fuzzy extractor.
